Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-02-28 apj.tex
fix caption

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/coeff0.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ are to guide the eye.
            \label{global1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/coeff1.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band.
 \label{global2:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/coeff2.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band.
 \label{global3:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output11/coeff3.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band.
 \label{global4:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
         \includegraphics[width=5.2in]{output11/coeff4.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band.
 \label{global5:fig}}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/residual.pdf} 
            \caption{Difference between predicted versus observed colors versus the observed color.
            \label{residual:fig}}
\end{figure}

@@

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\gamma$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.82 \\
0.72 & -5.27
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual vectors
\begin{align}
\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\end{align}
contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.

@@

Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
Our analysis yields an angle of 154\arcdeg between  $\gamma^0$ and $\gamma^1$.
The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.

@@

\section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
\label{model2:sec}
In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
two extrinsic parameters produce
magnitudes consistent
with two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
An extension to our model is now added to explore the possibility of
a possible additional
color parameter that could have its origins in supernova astrophysics.
The extended model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} + \delta_0 D\\
c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si} + \delta_1 D \\
c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} + \delta_2 D\\
c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} + \delta_3 D\\
c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{U} k_0 +\gamma^1_{B} k_1 \\B +\gamma^0_{B} k_0 +\gamma^1_{B} k_1 \\
V+\gamma^0_{V} k_0+\gamma^1_{V} k_1\\R+\gamma^0_{R} k_0 + \gamma^1_{R} k_1\\I+\gamma^0_{I} k_0+\gamma^1_{I} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$,
which affects the mean
absolute magnitudes:
each supernova has an intrinsic $D$ parameter that is linearly related to
absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
its effects on broadband magnitudes.

\color{red}
For $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1242 top-level parameters.
\color{black}

\color{red}
The $\delta D$ terms contribute to the mean of the Normal distribution in Eqn.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
it is for this reason that for convenience these terms are referred to as ``intrinsic''.
However, we emphasize now that we have also run the alternative case  of placing the
$\delta D$ terms in mean of the Normal distribution in Eqn.~\ref{dust:eqn}, i.e.\ as extrinsic contributions.
Analyses of the two different models give practically identical results, meaning that data are not constraining enough
to identify $\delta D$ as being physically intrinsic or extrinsic.
\color{black}

To constrain the new degrees of freedom and degeneracies inherent in the model we impose that
$D+1/N$ be a simplex to break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,  \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
\end{equation}
The first constraint specifies the definition of zero color.   The latter two confine possible magnitude
variations to those that cannot be attributed to 
the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
and $\gamma k$. 
Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_0$,
so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
\color{blue}
We apply the condition $\delta_4>0$ to break this degeneracy,
and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
\color{black}
In the running of the Monte Carlo, the initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
to maintain their correspondence between the two models.

The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the slight reduction of the standard
deviations of the magnitude residuals.
The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust model, in that now
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.22 & 2.73 \\
0.77 & -4.98
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the residual vectors 
\color{red}
\begin{align}
\vec{\epsilon}_a &=\{0.13, -0.15, -0.06,  0.04,  0.06\},\\
\vec{\epsilon}_b &=\{ -0.04, 0.09,  -0.18,  0.28, -0.19\}
\end{align}
\color{black}
are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
contribute similar 3\% and 4\% to the total  length of the vector.
%The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.

@@

$\alpha_X$
&
$0.0045^{+0.0009}_{-0.0010}$
&
$0.0017^{+0.0008}_{-0.0008}$
&
$0.0015^{+0.0006}_{-0.0006}$
&
$0.0015^{+0.0005}_{-0.0005}$
&
$0.0027^{+0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{+   1.1}_{  -0.5}$
&
$   0.1^{+   0.1}_{  -0.2}$
&
$  \ldots$
&
$   0.0^{+   0.1}_{  -0.1}$
&
$   0.8^{+   0.8}_{  -0.3}$
\\
$\beta_X$
&
$ 0.033^{+ 0.003}_{-0.003}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.021^{+ 0.002}_{-0.002}$
&
$ 0.020^{+ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.25^{+  0.04}_{ -0.05}$
&
$ -0.01^{+  0.02}_{ -0.03}$
&
$  \ldots$
&
$ -0.19^{+  0.01}_{ -0.01}$
&
$ -0.24^{+  0.03}_{ -0.03}$
\\
$\eta_X$
&
$0.0002^{+0.0012}_{-0.0012}$
&
$0.0002^{+0.0010}_{-0.0010}$
&
$0.0007^{+0.0008}_{-0.0008}$
&
$0.0007^{+0.0007}_{-0.0007}$
&
$0.0000^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.25^{+  1.35}_{ -1.38}$
&
$ -0.34^{+  1.21}_{ -1.04}$
&
$  \ldots$
&
$ -0.05^{+  0.34}_{ -0.29}$
&
$ -0.70^{+  0.84}_{ -0.88}$
\\
$\gamma^0_X$
&
$ 64.01^{+  3.79}_{ -3.69}$
&
$ 51.96^{+  3.18}_{ -3.10}$
&
$ 38.49^{+  2.70}_{ -2.63}$
&
$ 29.38^{+  2.40}_{ -2.33}$
&
$ 20.86^{+  2.19}_{ -2.22}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{+  0.06}_{ -0.05}$
&
$  0.35^{+  0.03}_{ -0.03}$
&
$  \ldots$
&
$ -0.24^{+  0.01}_{ -0.02}$
&
$ -0.46^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$-10.18^{+  3.53}_{ -3.92}$
&
$-11.64^{+  2.95}_{ -3.23}$
&
$-14.42^{+  2.45}_{ -2.72}$
&
$-13.73^{+  2.09}_{ -2.31}$
&
$-12.70^{+  2.03}_{ -2.16}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.29^{+  0.16}_{ -0.18}$
&
$ -0.19^{+  0.09}_{ -0.10}$
&
$  \ldots$
&
$ -0.05^{+  0.05}_{ -0.04}$
&
$ -0.12^{+  0.10}_{ -0.09}$
\\
$\delta_X$
&
$  2.07^{+  0.69}_{ -0.74}$
&
$ -2.25^{+  0.78}_{ -0.66}$
&
$ -1.85^{+  0.63}_{ -0.60}$
&
$  0.41^{+  0.53}_{ -0.57}$
&
$  2.02^{+  0.97}_{ -1.08}$
\\
${{\delta_X/\delta_I-1}}$
&
$  0.04^{+  0.52}_{ -0.27}$
&
$ -2.09^{+  0.27}_{ -0.62}$
&
$ -1.92^{+  0.25}_{ -0.56}$
&
$ -0.80^{+  0.68}_{ -0.26}$
&
$  \ldots$
\\
$\sigma_X$
&
$ 0.053^{+ 0.013}_{-0.012}$
&
$ 0.029^{+ 0.008}_{-0.009}$
&
$ 0.018^{+ 0.004}_{-0.005}$
&
$ 0.009^{+ 0.007}_{-0.006}$
&
$ 0.042^{+ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters of the Extrinsic--Intrinsic Model in \S\ref{model2:sec}.\label{global2:tab}}
\end{table}

@@

An interesting feature
is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
to $I$.
These are not the behaviors expected from normal dust,
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G} and so may be indicative of underlying supernova physics beyond that captured by $EW_{Ca}$, $EW_{Si}$ and
$\lambda_{Si}$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output23/delta_corner.pdf}
   \caption{Significance of the non-zero values of $\delta$ seen through the posterior contours for $\delta$.
   \label{deltacorner:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output23/deltaratio.pdf}
   \caption{Significance of the non-zero values of $\delta$ seen through $\delta_X/\delta_I-1$.
   \label{deltaratio:fig}}
\end{figure}

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/coeff0.pdf} 
            \caption{Model~I posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $U$ band.
            The contours shown here and in future plots represent 1-$\sigma$ in the parameter distribution (i.e.\ they should be
            projected onto the corresponding 1-d parameter axis), not to 68\%, 95\%, etc.\
            enclosed probability.  Lines for zero value for $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ are to guide the eye.
            \label{global1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/coeff1.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $B$ band, from Model~I.
 \label{global2:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/coeff2.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $V$ band, from Model~I.
 \label{global3:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output11/coeff3.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $R$ band, from Model~I.
 \label{global4:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
         \includegraphics[width=5.2in]{output11/coeff4.pdf} 
            \caption{Posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$, and $\sigma$ in the $I$ band, from Model~I.
 \label{global5:fig}}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/residual.pdf} 
            \caption{Differences between predicted versus observed colors versus the observed color.  For each color, the ideogram of the color differences is
            shown on the right.
            \label{residual:fig}}
\end{figure}

@@

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\gamma$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.82 \\
0.72 & -5.27
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\label{trans_I:eqn}
\end{equation}
where the two residual vectors
\begin{align}
\vec{\epsilon}_a &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_b & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\label{res_I:eqn}
\end{align}
contribute  2\% and 5\% respectively to the total  length of the $\gamma$ vectors.

@@

Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
Our analysis yields an angle of 154\arcdeg between  $\gamma^0$ and $\gamma^1$.
The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\gamma^0$.

@@

\section{Supernova Model II: Two Extrinsic Parameters, One Intrinsic Parameter}
\label{model2:sec}
In \S\ref{model:sec} we show that the SNfactory data analyzed with an agnostic model with
two extrinsic parameters produce
magnitudes consistent
with two-parameter dust models that have been established for stars in the Milky Way, LMC, and SMC.
An extension to our model is now added to explore the possibility of
a possible additional
color parameter that could have its origins in supernova astrophysics.
The extended model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_U+\alpha_U EW_{Ca} + \beta_U EW_{Si} + \eta_U \lambda_{Si} + \delta_U D\\
c_B+\alpha_B EW_{Ca} + \beta_B EW_{Si} + \eta_B \lambda_{Si} + \delta_B D \\
c_V+\alpha_V EW_{Ca} + \beta_V EW_{Si} + \eta_V \lambda_{Si} + \delta_V D\\
c_R+\alpha_R EW_{Ca} + \beta_R EW_{Si} + \eta_R \lambda_{Si} + \delta_R D\\
c_I+\alpha_I EW_{Ca} + \beta_I EW_{Si}+ \eta_I \lambda_{Si} + \delta_I D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{U} k_0 +\gamma^1_{B} k_1 \\B +\gamma^0_{B} k_0 +\gamma^1_{B} k_1 \\
V+\gamma^0_{V} k_0+\gamma^1_{V} k_1\\R+\gamma^0_{R} k_0 + \gamma^1_{R} k_1\\I+\gamma^0_{I} k_0+\gamma^1_{I} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$,
which affects the mean
absolute magnitudes.  Thus
each supernova is given an intrinsic $D$ parameter that is linearly related to
absolute magnitudes through global coefficients $\delta$.  As with $k_0$ and $k_1$,  $D$ is a latent supernova parameter whose existence is inferred from
its effects on broadband magnitudes.

\color{red}
In Model II, for $N$ supernovae there are $8N$ observables.  For the top-level model parameters, there are $3N$ spectral parameters, $3(N-2)$
color parameters, $(N-1)$ magnitude offsets,  $5 \times 7$ global coefficients, and $10$ parameters that describe the intrinsic
$C_c$.  For $N=172$ supernovae, there are 1376 observables and 1242 top-level parameters.
\color{black}

\color{red}
The $\delta D$ terms contribute to the mean of the Normal distribution in Eq.~\ref{ewsiv:eqn}, together with the spectral-feature terms:
it is for this reason that for convenience these terms are referred to as ``intrinsic''.
However, we emphasize now that we have also run the alternative case  of switching the placement of the
$\delta D$ terms from Eq.~\ref{ewsiv:eqn} to Eq.~\ref{dust:eqn}, i.e.\ from intrinsic to extrinsic contributions.
Analyses of the two different models give practically identical results, meaning that data are not constraining enough
to identify $\delta D$ as being physically intrinsic or extrinsic.
\color{black}

To constrain the new degrees of freedom and degeneracies inherent in the model we impose additional constraints.  We first
require that
$D+1/N$ be a simplex to break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,\,  \delta \cdot \gamma^0=0,\, \delta \cdot \gamma^1=0.
\end{equation}
The first of these constraints specifies the definition of zero color.   The latter two confine possible magnitude
variations to be those that cannot be attributed to 
the $\gamma k$ terms (i.e.\ dust); this condition breaks the degeneracies between $\delta D$  
and $\gamma k$. 
Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_U$,
so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
\color{blue}
We apply the condition $\delta_I>0$ to break this degeneracy,
and assume a flat prior for the three linear components of the subspace perpendicular to the $\gamma$ plane.
\color{black}
In the running of the Monte Carlo fit, the initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}
to maintain their correspondence between the two models.

The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that  parameters that are common to both
are consistent well within 1$\sigma$ uncertainties.  The most significant change is in the slight reduction of the standard
deviations of the magnitude residuals $\sigma_X$.
The newly fitted $\gamma$ parameters have an almost identical association with the  \citetalias{1999PASP..111...63F} dust model, in that now
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.15 & 2.79 \\
0.71 & -4.95
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the residual vectors 
\color{red}
\begin{align}
\vec{\epsilon}_a &=\{0.05, -0.06, -0.06,  0.06,  0.07\},\\
\vec{\epsilon}_b &=\{ -0.10, 0.20,  -0.19,  0.32, -0.30\}
\end{align}
\color{black}
are perpendicular to the  \citetalias{1999PASP..111...63F} plane and
contribute similar 2\% and 4\% to the total  length of the vector.
(These can be compared to the results of Model I in Eqs.\ \ref{trans_I:eqn}--\ref{res_I:eqn}.)
%The effective total-to-selective extinction for the supernova sample has a slight shift to $R^F_V=2.23 \pm 0.16$.

@@

$\alpha_X$
&
$0.0045^{+0.0009}_{-0.0010}$
&
$0.0017^{+0.0008}_{-0.0008}$
&
$0.0015^{+0.0006}_{-0.0006}$
&
$0.0015^{+0.0005}_{-0.0005}$
&
$0.0027^{+0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{+   1.1}_{  -0.5}$
&
$   0.1^{+   0.1}_{  -0.2}$
&
$  \ldots$
&
$   0.0^{+   0.1}_{  -0.1}$
&
$   0.8^{+   0.8}_{  -0.3}$
\\
$\beta_X$
&
$ 0.033^{+ 0.003}_{-0.003}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.021^{+ 0.002}_{-0.002}$
&
$ 0.020^{+ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.25^{+  0.04}_{ -0.05}$
&
$ -0.01^{+  0.02}_{ -0.03}$
&
$  \ldots$
&
$ -0.19^{+  0.01}_{ -0.01}$
&
$ -0.24^{+  0.03}_{ -0.03}$
\\
$\eta_X$
&
$0.0002^{+0.0012}_{-0.0012}$
&
$0.0002^{+0.0010}_{-0.0010}$
&
$0.0007^{+0.0008}_{-0.0008}$
&
$0.0007^{+0.0007}_{-0.0007}$
&
$0.0000^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.25^{+  1.35}_{ -1.38}$
&
$ -0.34^{+  1.21}_{ -1.04}$
&
$  \ldots$
&
$ -0.05^{+  0.34}_{ -0.29}$
&
$ -0.70^{+  0.84}_{ -0.88}$
\\
$\gamma^0_X$
&
$ 64.01^{+  3.79}_{ -3.69}$
&
$ 51.96^{+  3.18}_{ -3.10}$
&
$ 38.49^{+  2.70}_{ -2.63}$
&
$ 29.38^{+  2.40}_{ -2.33}$
&
$ 20.86^{+  2.19}_{ -2.22}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{+  0.06}_{ -0.05}$
&
$  0.35^{+  0.03}_{ -0.03}$
&
$  \ldots$
&
$ -0.24^{+  0.01}_{ -0.02}$
&
$ -0.46^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$-10.18^{+  3.53}_{ -3.92}$
&
$-11.64^{+  2.95}_{ -3.23}$
&
$-14.42^{+  2.45}_{ -2.72}$
&
$-13.73^{+  2.09}_{ -2.31}$
&
$-12.70^{+  2.03}_{ -2.16}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.29^{+  0.16}_{ -0.18}$
&
$ -0.19^{+  0.09}_{ -0.10}$
&
$  \ldots$
&
$ -0.05^{+  0.05}_{ -0.04}$
&
$ -0.12^{+  0.10}_{ -0.09}$
\\
$\delta_X$
&
$  2.07^{+  0.69}_{ -0.74}$
&
$ -2.25^{+  0.78}_{ -0.66}$
&
$ -1.85^{+  0.63}_{ -0.60}$
&
$  0.41^{+  0.53}_{ -0.57}$
&
$  2.02^{+  0.97}_{ -1.08}$
\\
${{\delta_X/\delta_I-1}}$
&
$  0.04^{+  0.52}_{ -0.27}$
&
$ -2.09^{+  0.27}_{ -0.62}$
&
$ -1.92^{+  0.25}_{ -0.56}$
&
$ -0.80^{+  0.68}_{ -0.26}$
&
$  \ldots$
\\
$\sigma_X$
&
$ 0.053^{+ 0.013}_{-0.012}$
&
$ 0.029^{+ 0.008}_{-0.009}$
&
$ 0.018^{+ 0.004}_{-0.005}$
&
$ 0.009^{+ 0.007}_{-0.006}$
&
$ 0.042^{+ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters of the Extrinsic--Intrinsic Model~II in \S\ref{model2:sec}.\label{global2:tab}}
\end{table}

@@

An interesting feature
is that the shift in magnitude is not monotonic in wavelength, but rather decreases from $U$ to $V$, and then increases from $V$
to $I$.
These are not the behaviors expected from normal dust, or
circumstellar dust suggested as a source of SN extinction \citep{2005ApJ...635L..33W,2008ApJ...686L.103G,
2015ApJ...807L..26G} and so may be indicative of underlying supernova physics beyond that captured by $EW_{Ca}$, $EW_{Si}$ and
$\lambda_{Si}$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output23/delta_corner.pdf}
   \caption{Significance of the non-zero values of $\delta$ as demonstrated by the posterior contours for $\delta$ for Model~II.
   Lines for $\delta=0$ are overplotted.
   \label{deltacorner:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output23/deltaratio.pdf}
   \caption{Significance of the non-zero values of $\delta$ as demonstrated by the best-fit values of $\delta_X/\delta_I-1$ for $\delta$ for Model~II.
   \label{deltaratio:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, $E_{\gamma^1}(B-V)$,  $A_{\delta I}=\delta_I D$ are given in the matrix.
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V),  A_{\delta I}) =\\
\begin{pmatrix}
\begin{array}{rrrrrrr}
1.00 & 0.00 & -0.07 & -0.04 & 0.11 & 0.01 & -0.06 \\
0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.02 & -0.02 \\
-0.07 & 0.10 & 1.00 & -0.14 & -0.17 & -0.04 & 0.04 \\
-0.04 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 & -0.07 \\
0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 & 0.06 \\
0.01 & -0.02 & -0.04 & 0.03 & 0.05 & 1.00 & 0.01 \\
-0.06 & -0.02 & 0.04 & -0.07 & 0.06 & 0.01 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}
The correlation coefficients between the ``intrinsic'' and ``extrinsic'' parameters are $0.06$ and $0.01$.
This has two important implications:
First, while in principle a single physical color effect can affect both intrinsic and extrinsic parameters, from the correlations
there is no evidence
that this occurs.
Second, the intrinsic term is not a second-order extrinsic correction.
